NURM: a tool to locate numerical differences in pipelines

### 2019-06-21 paper.tex
Comments on results

The HCP developed a set of pre-processing pipelines to process structural,
functional and diffusion MRI data acquired in the project. We focus on HCP
pre-processing pipelines for structural data, particularly PreFreeSurfer
and FreeSurfer. A detailed description of the analyses done in the
pipelines is available in~\cite{glasser2013}.
% IF NEEDED, ADD MORE DETAILS ABOUT WHAT THE PIPELINES DO
% The structural pre-processing pipelines consists of PreFreeSurfer, 
% FreeSurfer and PostFreeSurfer. In this paper, 
% we analyzed PreFreeSurfer pipeline which consist of various steps 
% including correction of MR 
% gradient nonlinearity distortions, align the T1w and T2w images using 
% FSL FLIRT, Align native space to MNI template using ACPC and FSL FLIRT, 
% brain extraction usin FSL FLIRT and FNIRT to MNI template, register T2w 
% to T1w using FLIRT's BBR, perform a bias field correction, and register 
% the subject's native structural space to MNI space.
In this paper, we randomly selected 100 unprocessed subjects from the HCP data release S500.
We first quantify the effect of Linux version on
these pipelines. Then we identify the processes in the
pipelines that are responsible for such effects using NURM-tool.

@@

\subsection{Results}

We executed the pipelines using Docker containers to simplify the 
deployment of different operating system versions on execution 
platforms. The Docker images were built for the HCP pre-processing 
pipelines v3.19.0 (PreFreeSurfer and FreeSurfer) in 
CentOS 6.8 and CentOS 7.2. Docker images are available on 
\href{https://hub.docker.com/r/bigdatalabteam/hcp-prefreesurfer/}{DockerHub}
for reuse.

Two types of errors can occur in the subjects due to the 
errors in the operating systems. One is inter-OS error caused by the 
operating system library updates and the other type, intra-OS errors 
occurs as a result of the pseudo-random processes used in the 
pipelines. 
We have initialized random number generators using a seed state 
to avoid intra-OS errors in our experiments. 
Therefore, NURM-tool is able to identify the process in the pipelines 
that create differences caused by the inter-OS errors.

@@

In the previous study~\cite{Scaria2017}, we showed that the HCP pre-processing 
pipelines~\cite{glasser2013} were 
sensitive to operating system variation so that Figure 
\ref{fig:tissue_class} illustrates the binarized differences after brain 
tissue segmentation process in FreeSurfer. In addition, 
Figure~\ref{fig:fnirt_result} shows the same differences occurred in 
non-linear registration process between CentOS6 and CentOS7 in PreFreeSurfer.

@@

We clustered subjects into different groups using the NURM-tool, 
after that PreFreeSurfer pipeline has executed on input data.
Figure~\ref{fig:subj-clusters} shows the result of data clustering. 
Among our dataset, we identified 4 types of subjects with 
different topology of \emph{process trees}. In addition, we verified that 
the \emph{process trees} were identical for all subjects of the same type in 
different versions of CentOS operating system.

>>>>

The HCP developed a set of pre-processing pipelines to process structural,
functional and diffusion MRI data acquired in the project. We focus on HCP
pre-processing pipelines for structural data, particularly PreFreeSurfer
and FreeSurfer. A detailed description of the analyses done in the
pipelines is available in~\cite{glasser2013}. \TG{Introduce and present all the
pipeline components mentioned in the results, such as BrainExtraction, ACPC alignment, \ldots
The presentation should be at the right level of detail.}
% IF NEEDED, ADD MORE DETAILS ABOUT WHAT THE PIPELINES DO
% The structural pre-processing pipelines consists of PreFreeSurfer, 
% FreeSurfer and PostFreeSurfer. In this paper, 
% we analyzed PreFreeSurfer pipeline which consist of various steps 
% including correction of MR 
% gradient nonlinearity distortions, align the T1w and T2w images using 
% FSL FLIRT, Align native space to MNI template using ACPC and FSL FLIRT, 
% brain extraction usin FSL FLIRT and FNIRT to MNI template, register T2w 
% to T1w using FLIRT's BBR, perform a bias field correction, and register 
% the subject's native structural space to MNI space.
In this paper, we randomly selected 100 unprocessed subjects from the HCP data release S500.
We first quantify the effect of Linux version on
these pipelines. Then we identify the processes in the
pipelines that are responsible for such effects using NURM-tool.

@@

\section{Results}

We executed the pipelines using Docker containers to simplify the 
deployment of different operating system versions on execution 
platforms. The Docker images were built for the HCP pre-processing 
pipelines v3.19.0 (PreFreeSurfer and FreeSurfer) in 
CentOS 6.8 and CentOS 7.2. Docker images are available on 
\href{https://hub.docker.com/r/bigdatalabteam/hcp-prefreesurfer/}{DockerHub}
for reuse. \TG{Should go to experiments}

Two types of errors can occur in the subjects due to the 
errors in the operating systems. One is inter-OS error caused by the 
operating system library updates and the other type, intra-OS errors 
occurs as a result of the pseudo-random processes used in the 
pipelines. 
We have initialized random number generators using a seed state 
to avoid intra-OS errors in our experiments \TG{how? where?}. 
Therefore, NURM-tool is able to identify the process in the pipelines 
that create differences caused by the inter-OS errors. \TG{Change errors to differences.}
\TG{Check that again, on all subjects.}

@@

In a previous study~\cite{Scaria2017}, we showed that the HCP pre-processing 
pipelines~\cite{glasser2013} were 
sensitive to operating system variation. Figure 
\ref{fig:tissue_class} illustrates the binarized differences after brain 
tissue segmentation in FreeSurfer. In addition, 
Figure~\ref{fig:fnirt_result} shows the same differences after 
non-linear in PreFreeSurfer.

@@

We clustered subjects into different groups using the NURM-tool, 
after that PreFreeSurfer pipeline has executed on input data.
Figure~\ref{fig:subj-clusters} shows the result of data clustering. \TG{Make a table instead of a figure. 
Mention the threshold and any other clustering parameter.}
Among our dataset, we identified 4 types of subjects with 
different topology of \emph{process trees}. In addition, we verified that 
the \emph{process trees} were identical for all subjects of the same type in 
different versions of CentOS operating system. \TG{Check what these 4 types correspond to}
